\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fontawesome5}

% Custom Colors
\definecolor{oncoBlue}{RGB}{0, 51, 102}
\definecolor{heading}{RGB}{0, 51, 102}
\definecolor{accent}{RGB}{100, 100, 100}

% Title Formatting
\titleformat{\section}{\large\bfseries\color{heading}}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\LARGE\bfseries\color{heading} MUHAMMAD OSAMA}\\[3pt]
    {\normalsize\color{accent}Software Engineer -- Python}\\[4pt]
    \small
    \faEnvelope\ \href{mailto:ocama_aslam@outlook.com}{ocama\_aslam@outlook.com} \quad
    \faPhone\ +92\,327\,293\,1163 \quad
    \faGithub\ \href{https://github.com/OcamaAslam}{OcamaAslam} \quad
    \faLinkedin\ \href{https://linkedin.com/in/ocama-mohamed}{ocama-mohamed} \quad
    \faGlobe\ \href{https://www.artfolio.tech/osama}{Portfolio}
\end{center}

\vspace{1em}
\begin{center}
    {\huge\bfseries\color{heading} OncoGraph X: Project Proposal} \\
    {\large\color{accent} Explainable Clinical Twin Analytics for Precision Oncology}
\end{center}
\vspace{1.5em}

\section{Executive Summary}
OncoGraph X is a Clinical Decision Support System (CDSS) designed to enhance cancer recurrence and survival prediction. The platform utilizes an \textbf{Explainable Clinical Twin (XCT)} architecture, leveraging Graph Neural Networks (GNNs) to identify historical patients with similar profiles. This provides oncologists with transparent, evidence-based predictions grounded in comparative clinical data.

\section{The Clinical Twin Methodology}
The core innovation of OncoGraph X is the \textbf{Patient Similarity Graph}. Unlike traditional models that treat patients as isolated data points, OncoGraph X models the relationships between them:
\begin{itemize}[noitemsep]
    \item \textbf{Network Construction:} Patients are connected in a graph based on shared clinical markers, such as Primary Tumor Site and Pathological T-Stage.
    \item \textbf{Weighted Similarity:} Connections are weighted based on the proximity of histological grading and nodal status (pN-Stage).
    \item \textbf{Multi-modal Integration:} The system integrates 22 features across blood work, pathological reports, and patient demographics.
\end{itemize}

\section{Technical Architecture}
The system utilizes a dual-task \textbf{GraphSAGE Encoder} architecture to process patient data:
\begin{enumerate}[noitemsep]
    \item \textbf{Feature Aggregation:} The GNN aggregates insights from a patient's ``twins'' to derive a robust risk profile.
    \item \textbf{Dual Prediction Heads:} Simultaneously predicts recurrence probability and estimated survival scores.
    \item \textbf{Explainability Engine:} Highlights specific clinical markers (e.g., blood protein levels) that most significantly influence a patient's specific prediction.
\end{enumerate}

\section{Key Features}
\begin{itemize}
    \item \textbf{Clinical Twin Dashboard:} Interactive visualization of patient proximity and historical outcomes.
    \item \textbf{Feature Importance:} Transparent breakdown of the clinical drivers behind every risk score.
    \item \textbf{Interactive Risk Assessment:} Real-time updates of risk scores based on adjustable clinical inputs.
    \item \textbf{Evidence-Based Reporting:} Identification of specific historical cases that justify the model's output.
\end{itemize}

\section{Data Disclosure}
\textbf{Note:} All clinical data, patient statistics, and performance benchmarks referenced in this project were generated using \textbf{synthetic statistical methods}. This synthetic dataset is designed to mimic real-world oncological patterns for research, development, and demonstration purposes while maintaining absolute data privacy.

\section{Conclusion}
OncoGraph X bridges the gap between complex AI and clinical intuition. By anchoring predictions in the ``Clinical Twin'' framework, it offers a transparent path forward for high-stakes medical decision-making.

\end{document}
